Notation proposal

### 2011-05-31 notation.tex
fixed interp decimate functions
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@793 ccdd05d5-56c1-461a-bf98-85f6876523b4

Throughout, we will use the convention that $k$ indexes time-series sampled at
the full sample rate $f$ and $k^s$ indexes time-series sampled at a reduced
sample rate $f^s$, ($k^{s} \equiv k f \ f^{s}$).  For the case of band limited
functions it is sufficient to simply remove sample points to define the
downsampled version as is shown in the previous equation.

>>>>

Throughout, we will use the convention that $k$ indexes time-series sampled at
the full sample rate $f$ and $k^s$ indexes time-series sampled at a reduced
sample rate $f^s$, ($k^{s} \equiv k f / f^{s}$).  For the case of band limited
functions it is sufficient to simply remove sample points to define the
downsampled version as is shown in the previous equation.
